\begin{rubric}{\small Experience}
 \entry*[April 2024 --present]%
	\textbf{Consultant}: Laboratory for Energy And Power Solutions (\href{https://leaps.asu.edu/newprojectspage/}{LEAPS}), Arizona, US.
Working on Madagascar Integrated Energy Planning. Clean cooking analysis component of integrated energy plan to provide clean and affordable energy access to all in Madagascar by 2030.
\entry*[2021 -- 2024]%
	\textbf{Associate Researcher}: \href{http://www.chair-energy-prosperity.org/en/category/research-fellows-1/mboundor-diouf-en/}{Energy and Prosperity Chair}, \href{https://www.cerna.minesparis.psl.eu/Equipe/Doctorant-e-s/Mboundor-Diouf/}{EIEA Chair (CERNA and UM6P)}, \href{https://i3.cnrs.fr/membres/}{Institut interdisciplinaire de l'innovation (Mines Paristech)}, \href{https://crs-g5-sahel.com/team/diouf-mboundo/}{the CR-Sahel}.
 \entry*[2018 -- present]%
	\textbf{Lecturer in Economics}, 
Sept-December 2024: University of Poitiers. Sept 2022-present: University of Paris 1 Panthéon-Sorbonne. 2018-2019: Clermont Auvergne University.
% \entry*[Jan 2023--Jul 2023]%
%	\textbf{Consultant}: Centre de Reflexion pour le Sahel (CR-Sahel), Burkina Faso.
 \entry*[Jan 2022--Aug 2022]%
	\textbf{Consultant}: Chair Energy and Prosperity, Paris, France.
\entry*[Fev 2021--Jul 2021]%
	\textbf{Intern}, CERNA (Mines ParisTech), Paris (France).\par
 Training on energy and mining exploitation. Analytical and Quantitative methods used in economic research.\par
 Supervisor: \emph{Pierre Noel Giraud} 
\entry*[2018 -- 2019]%
	\textbf{Intern, 
Research Study Assistant}, Clermont Auvergne University -
CERDI, Clermont-Ferrand (France).\par
Modeling and analysis of African climate data (mapping and interpretation) with Rstudio (R-shiny) and Quantum GIS.
\par Supervisor: \emph{Catherine Araujo Bonjean} 
\end{rubric}
